AggregateCounts

### 2021-06-28 R/AggregateCounts.Rmd
added z-slice figure

```{r biomass per slice}
#this was taken from "Microscopy data clean.Rmd"
GetResults<-function(){
  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images'
  samplesList<-list.files(path = folder, full.names = TRUE)
  imagesList<-mapply(list.files,samplesList)

separateColors
  blueChannel<-fileList[grep('B_',fileList)]
  redChannel<-fileList[grep('R_',fileList)]
  greenChannel<-fileList[grep('G_',fileList)]
  Results<-rbind(blueChannel,redChannel,greenChannel)
  Results<-Results %>% mutate(Sample = sample)

   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
     }
   return(growthDf)
}

@@

  IterateTiff<-function(fileList, species)
  growth<-matrix(ncol=3, nrow=length(fileList))
  for(slice in 1:(length(fileList))){
    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
    growth[slice,]<-c(counts, slice, species)
  }
  growthDf<-data.fram(growth)
return(growthDf) 
  }

>>>>

```{r biomass per slice}
#this was taken from "Microscopy data clean.Rmd" 
GetSliceData<-function(){#import all experiments at once
  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice'
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadSliceFile(fileList[aggList],attrList[2],attrList[1],attrList[3], fileName))
     }
   return(growthDf)
}

ReadSliceFile<-function(file, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
  print(file)
   datos <-read.csv(file, header = F)  
   colnames(datos)<-c('Biomass', 'Channel', 'Slice') 
   datos<-datos %>% mutate(TimePoint = timepoint) 
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos<-datos %>% mutate(SampleCode = sampleCode)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   return(datos)
}

slicedData<-GetSliceData()

#merge with metadata
metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/image data copy.csv', header = TRUE)

metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Voxel.size,Region, Zdim)
sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
sliceDataMeta <- anti_join(sliceDataMeta, remove)

sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
sliceDataMeta<-sliceDataMeta %>% mutate(Height = Zdim*Slice)
sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)

ggplot()+
  geom_point(data = sliceDataMeta,aes(x=NormBiomass,y=Height, color = Condition, shape = TimePoint ),size=2)+

  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  facet_grid(Channel~Condition)+
  theme(plot.title = element_text(hjust = 0.5))

```{r read Tiff functions}

@@

  IterateTiff<-function(fileList, species){
  growth<-matrix(ncol=3, nrow=length(fileList))
  for(slice in 1:(length(fileList))){
    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
    growth[slice,]<-c(counts, slice, species)
  }
  growthDf<-data.fram(growth)
return(growthDf) 
  }
